---
title: "Data wrangling for Multi-Level Analysis of Foster Care as an Alternative to Institutionalization on Biobehavioral Outcomes Across Childhood"
date: "2021"
output: 
  github_document:
    toc: true
    toc_depth: 2
---

https://docs.google.com/spreadsheets/d/1TubH73N8ZpJwILDFGZ6qtvvQM0gqGrzcYEVapVomFaQ/edit?ts=5e0e38bf#gid=0

```{r}
library(tidyverse)
library(labelled)

#Files__________________________________________________________________________
home <- "~/Desktop/Tulane/BEIP/comprehensive_analysis/"

# Demographics, IQ, psychopathology, physical size
BEIP_MA_file <- paste0(home, "data/Datarequest_Humphreys_12.7.19_updated.sav")
RAD_12yr_file <- paste0(home, "data/RAD_age12.sav")

# FC stability 
stability_file <- paste0(home, "data/BEIP_18yrDisruptionsStabilityFCG.xlsx")

# EEG 
EEG_ages_file <- paste0(home, "data/All EEG ages.sav")
EEG_16yr_age_file <- paste0(home, "data/ages16eeg_update.sav") # 16 yr wave EEG age incorrect in main file; use age in file below
EEG_data_file <- paste0(home, "data/BEIP_30mo-16yr_rel_alpha_power_021122.csv")

# sibling information
sibling_file <- paste0(home, "data/BEIP_siblings_info.csv")
```

# Read in data

```{r}
d0 <- 
  haven::read_sav(BEIP_MA_file) %>% 
  rename(
    ID = Subject,
    bl_age_start = bslevalAgeM, # age in months at first baseline assessment
    bl_age_end = FinEvalAgeM, # age in months at last baseline assessment
    sex = Gender,
    group = Group
  ) %>% 
  left_join(
    readxl::read_xlsx(stability_file, sheet = "data") %>% 
      dplyr::select(
        ID = SUBJECT,
        stability_18 = stable_MFC_18,
        age_disrupt_days = age_disruption_fromFCG
      ),
    by = "ID"
  )
```

## EEG data

### Clean ages of EEG assessments
```{r}
eeg_ages <-
  haven::read_sav(EEG_ages_file) %>% 
  rename(
    ID = Subject
  ) %>%
  dplyr::select(-EEG_ageM_16, -EEG_ageY_16) %>% 
  left_join(d0 %>% dplyr::select(ID, bl_age_end), by = "ID") %>% 
  left_join(
    haven::read_sav(EEG_16yr_age_file) %>% 
      dplyr::select(
        ID = Subject,
        EEG_ageM_16 = ageM_EEG_16
      ),
    by = "ID"
  ) %>% 
  gather(
    eeg_key, 
    age, 
    EEG_ageM_0, EEG_ageM_1:EEG_ageM_5, EEG_ageM_8, EEG_ageM_12, EEG_ageM_16
  ) %>% 
  dplyr::select(-c(EEG_ageY_8:EEG_ageY_12)) %>% 
  separate(eeg_key, into = c("domain", "x", "eeg_key")) %>% 
  dplyr::select(-x) %>% 
  mutate_all(str_to_lower) %>% 
  mutate_at(
    vars(ID, bl_age_end, age),
    as.double
  ) %>% 
  mutate(
    age_diff_BL = abs(age - bl_age_end),
    age_diff_30 = abs(age - 30),
    age_diff_42 = abs(age - 42)
  ) %>% 
  group_by(ID) %>% 
  mutate(
    min_age_diff = pmin(
      age_diff_BL, 
      age_diff_30, 
      age_diff_42
    )
  ) %>% 
  mutate(
    # identify wave based on closest age 
    wave = case_when(
      eeg_key == "8" ~ "8",
      eeg_key == "12" ~ "12",
      eeg_key == "16" ~ "16",
      eeg_key == "0" ~ "BL",
      eeg_key == "1" & age >= 29 & age < 37 ~ "30",
      eeg_key == "1" & age >= 41 & age < 54 ~ "42",
      eeg_key == "2" & age >= 29 & age < 37 ~ "30",
      eeg_key == "3" & age >= 29 & age < 37 ~ "30",
      eeg_key == "4" & age >= 29 & age < 37 ~ "30",
      eeg_key == "2" & age >= 41 & age < 54 ~ "42",
      eeg_key == "3" & age >= 41 & age < 54 ~ "42",
      eeg_key == "4" & age >= 41 & age < 54 ~ "42",
      eeg_key == "5" & age >= 41 & age < 54 ~ "42"
    )
  ) %>% 
  arrange(ID) %>% 
  dplyr::select(ID, age, wave)
```   

### Reformat EEG data 

```{r}
eeg_data <-
  read_csv(EEG_data_file) %>% 
  rename(
    relalpha_30 = rel_alpha_mean_30mo,
    relalpha_42 = rel_alpha_mean_42mo,
    relalpha_8 = rel_alpha_mean_96mo,
    relalpha_12 = rel_alpha_mean_12yr,
    relalpha_16 = rel_alpha_mean_16yr
  ) %>% 
  gather(eeg_key, value, -ID) %>% 
  separate(eeg_key, c("measure", "wave")) %>% 
  mutate(
    domain = "eeg",
    informant = "O"
  ) %>% 
  filter(!is.na(value))
```

### Join EEG data with ages of assessment
```{r}
eeg <-
  eeg_data %>% 
  left_join(eeg_ages, by = c("ID", "wave")) %>% 
  filter(ID != "0", ID < 800) 
```

## ITSEA data

### Clean ITSEA ages of assessment
```{r}
# Use earliest observation as baseline. For subsequent, take closes to the intended wave.
itsea_ages <-
  d0 %>% 
  dplyr::select(
    ID,
    bl_age_end,
    starts_with("ageitsea")
  ) %>% 
  gather(itsea_key, age, ageitsea..00:ageitsea.5.00) %>% 
  mutate(
    itsea_key = recode(
      itsea_key,
      "ageitsea..00" = "0",
      "ageitsea.1.00" = "1",
      "ageitsea.2.00" = "2",
      "ageitsea.3.00" = "3",
      "ageitsea.4.00" = "4",
      "ageitsea.5.00" = "5"
    )
  ) %>% 
  mutate(
    age_diff_BL = abs(age - bl_age_end),
    age_diff_30 = abs(age - 30),
    age_diff_42 = abs(age - 42),
    age_diff_54 = abs(age - 54)
  ) %>% 
  group_by(ID) %>% 
  mutate(
    min_age_diff = pmin(
      age_diff_BL, 
      age_diff_30, 
      age_diff_42, 
      age_diff_54
    ),
    wave = case_when(
      min_age_diff == age_diff_BL ~ "0",
      min_age_diff == age_diff_30 ~ "30",
      min_age_diff == age_diff_42 ~ "42",
      min_age_diff == age_diff_54 ~ "54"
    ),
    wave = if_else(
      itsea_key == "0", "0", wave
    )
  ) %>% 
  filter(!is.na(age)) %>% 
  arrange(ID, wave, age) %>% 
  group_by(ID) %>% 
  mutate(
    wave = case_when(
      lag(wave) == "0" & wave == "0" ~ "30",
      is.na(wave) & itsea_key == "0" ~ "0",
      lead(wave) == "42" & wave == "42" & age < lead(age) ~ "drop",
      TRUE ~ wave
    ),
    wave = case_when(
      lead(wave) == "30" & wave == "30" & age < lead(age) ~ "drop",
      wave == "0" ~ "BL",
      TRUE ~ wave
    ),
    wave = if_else(
      wave == "30" & age < 20,
      "drop", wave
    )
  ) %>% 
  ungroup() %>% 
  filter(wave != "drop", !is.na(wave)) %>% 
  dplyr::select(-c(age_diff_BL:min_age_diff))
```  

### Reformat ITSEA data 
```{r}
itsea_domains <- 
  d0 %>% 
  dplyr::select(
    ID,
    starts_with("activmen"),
    starts_with("agdefmen"),
    starts_with("intermen")
  ) %>% 
  gather(
    itsea_key, 
    value, 
    activmen..00:intermen.5.00
  ) %>% 
  mutate(
    domain = case_when(
      str_detect(itsea_key, "activmen") == TRUE ~ "adhd",
      str_detect(itsea_key, "agdefmen") == TRUE ~ "extern",
      str_detect(itsea_key, "intermen") == TRUE ~ "intern"
    ),
    itsea_key = case_when(
      str_detect(itsea_key, "\\.\\.") == TRUE ~ "0",
      str_detect(itsea_key, "1") == TRUE ~ "1",
      str_detect(itsea_key, "2") == TRUE ~ "2",
      str_detect(itsea_key, "3") == TRUE ~ "3",
      str_detect(itsea_key, "4") == TRUE ~ "4",
      str_detect(itsea_key, "5") == TRUE~ "5"
    )
  ) 
```

### Join ITSEA data with ages of assesment
```{r}
itsea <-
  itsea_domains %>% 
  left_join(itsea_ages, by = c("ID", "itsea_key")) %>% 
  mutate(
    measure = "itsea",
    informant = "P"
  ) %>% 
  dplyr::select(-itsea_key, -bl_age_end) %>% 
  filter(!is.na(value), !is.na(wave))
```

    
## All other psychopathology, IQ, physical size

### Reformat data
```{r}
d0_domains <- 
  d0 %>% 
  group_by(ID) %>% 
  mutate(
    adhd_hbq_8_T = mean(c(HBQT8_Inatt, HBQT8_Impuls), na.rm = TRUE)
  ) %>% 
  dplyr::select(
    ID,
    adhd_hbq_8_T,
    adhd_disc_12_P = DISC_ADHDtotalP_12,
    adhd_hbq_12_P = HBQP12_ADHD,
    adhd_hbq_12_T = HBQT12_ADHD,
    adhd_disc_16_P = ADHDtotalP16,
    adhd_hbq_16_P = HBQP16_ADHD,
    adhd_hbq_16_T = HBQT16_ADHD,
    adhd_p4nadz_54_P = p4nadz,
    dsed_dai_8_P = raddis_8yr,
    dsed_dai_12_P = DAI_dis_12,
    dsed_dai_16_P = Inhibited_16y,
    dsed_dai_30_P = raddis_30c,
    dsed_dai_42_P = raddis_42c,
    dsed_dai_54_P = raddis_54c,
    dsed_dai_BL_P = raddis_blc,
    extern_hbq_8_T = HBQT8_Extern,
    extern_disc_12_P = DISC_ODDandCDP_12,
    extern_hbq_12_P = HBQP12_Extern,
    extern_hbq_12_T = HBQT12_Extern,
    extern_disc_16_P = ODDandCDtotalP16,
    extern_hbq_16_P = HBQP16_Extern,
    extern_hbq_16_T = HBQT16_Extern,
    extern_oddcdsx_54_P = oddcdsx,
    head_ofc_8_O = OFC_8yr,
    head_ofc_12_O = OFC_12yr,
    head_ofc_16_O = OFC_16yr,
    head_ofc_30_O = OFC_30mo,
    head_ofc_42_O = OFC_42mo,
    head_ofc_BL_O = OFC_BL,
    height_cm_8_O = height_8yr,
    height_cm_12_O = height_12yr,
    height_cm_16_O = height_16yr,
    height_cm_30_O = height_30mo,
    height_cm_42_O = height_42mo,
    height_cm_BL_O = height_BL,
    intern_hbq_8_T = HBQT8_Intern,
    intern_disc_12_P = DISC_inttotalP_12,
    intern_hbq_12_P = HBQP12_Intern,
    intern_hbq_12_T = HBQT12_Intern,
    intern_disc_16_P = inttotalnospphP16,
    intern_hbq_16_P = HBQP16_Intern,
    intern_hbq_16_T = HBQT16_Intern,
    intern_intsx_54_P = intsx,
    iq_wisc_8_O = FSISUMSC_8,
    iq_wisc_12_O = FSIQ_COMP_12,
    iq_wisc_16_O = IQ_fullscale_age18,
    iq_bayley_30_O = devquot_30mo,
    iq_bayley_42_O = devquot_42mo,
    iq_wppsi_54_O = fulliq,
    iq_bayley_BL_O = mdi_bl,
    rad_dai_8_P = radinh_8yr,
    rad_dai_12_P = DAI_inh_12,
    rad_dai_16_P = Disinhibited_16y,
    rad_dai_30_P = radinh_30c,
    rad_dai_42_P = radinh_42c,
    rad_dai_54_P = radinh_54c,
    rad_dai_BL_P = radinh_blc,
    weight_kg_8_O = weight_8yr,
    weight_kg_12_O = weight_12yr,
    weight_kg_16_O = weight_16yr,
    weight_kg_30_O = weight_30mo,
    weight_kg_42_O = weight_42mo,
    weight_kg_BL_O = weight_BL
  ) %>% 
  # incorrect RAD data at 12y; replace with data from KGH
  dplyr::select(-rad_dai_12_P) %>% 
  left_join(
    haven::read_sav(RAD_12yr_file) %>% 
      rename(
        rad_dai_12_P = Inhibited_12y
      ) %>% 
      dplyr::select(
        ID = subject,
        rad_dai_12_P
      ),
    by = "ID"
  ) %>% 
  gather(domain_key, value, adhd_hbq_8_T:last_col()) %>% 
  ungroup() %>% 
  filter(!is.na(value)) 
```

### Ages of assessment
```{r}
d0_ages <-
  d0 %>% 
  mutate(
    adhd_hbq_8_T = hbqt8_ageyrs * 12,
    adhd_disc_12_P = DISC_age_12 * 12,
    adhd_hbq_12_P = ageM_hbqp,
    adhd_hbq_12_T = ageM_hbqt,
    adhd_disc_16_P = ageDisc16 * 12,
    adhd_hbq_16_P = age_HBQ16p_M,
    adhd_hbq_16_T = age_HBQ16t_M,
    adhd_p4nadz_54_P = jage * 12,
    dsed_dai_8_P = ageM_8_dai,
    dsed_dai_12_P = ageM_12,
    dsed_dai_16_P = ageM_DAI16,
    dsed_dai_30_P = ageM_30_dai,
    dsed_dai_42_P = ageM_42_dai,
    dsed_dai_54_P = ageM_54_dai,
    dsed_dai_BL_P = ageM_bsl_dai,
    extern_hbq_8_T = hbqt8_agemos,
    extern_disc_12_P = DISC_age_12 * 12,
    extern_hbq_12_P = ageM_hbqp, 
    extern_hbq_12_T = ageM_hbqt, 
    extern_disc_16_P = ageDisc16 * 12,
    extern_hbq_16_P = age_HBQ16p_M,
    extern_hbq_16_T = age_HBQ16t_M,
    extern_oddcdsx_54_P = jage * 12,
    head_ofc_8_O = ageM_8yr,
    head_ofc_12_O = ageM_12yr,
    head_ofc_16_O = ageM_16yr_physical,
    head_ofc_30_O = ageM_30mo,
    head_ofc_42_O = ageM_42mo,
    head_ofc_BL_O = ageM_BL,
    height_cm_8_O = ageM_8yr,
    height_cm_12_O = ageM_12yr,
    height_cm_16_O = ageM_16yr_physical,
    height_cm_30_O = ageM_30mo,
    height_cm_42_O = ageM_42mo,
    height_cm_BL_O = ageM_BL,
    intern_hbq_8_T = hbqt8_agemos,
    intern_disc_12_P = DISC_age_12 * 12,
    intern_hbq_12_P = ageM_hbqp, 
    intern_hbq_12_T = ageM_hbqt, 
    intern_disc_16_P = ageDisc16 * 12,
    intern_hbq_16_P = age_HBQ16p_M,
    intern_hbq_16_T = age_HBQ16t_M,
    intern_intsx_54_P = jage * 12,
    iq_wisc_8_O = wisc8_agemos,
    iq_wisc_12_O = Age * 12,
    iq_wisc_16_O = Age_WISC_16 * 12,
    iq_bayley_30_O = age_bay_30mo,
    iq_bayley_42_O = age_bay_42mo,
    iq_wppsi_54_O = wppsiage,
    iq_bayley_BL_O = age_bay_bl,
    rad_dai_8_P = ageM_8_dai,
    rad_dai_12_P = ageM_12,
    rad_dai_16_P = ageM_DAI16,
    rad_dai_30_P = ageM_30_dai,
    rad_dai_42_P = ageM_42_dai,
    rad_dai_54_P = ageM_54_dai,
    rad_dai_BL_P = ageM_bsl_dai,
    weight_kg_8_O = ageM_8yr,
    weight_kg_12_O = ageM_12yr,
    weight_kg_16_O = ageM_16yr_physical,
    weight_kg_30_O = ageM_30mo,
    weight_kg_42_O = ageM_42mo,
    weight_kg_BL_O = ageM_BL
  ) %>% 
  dplyr::select(ID, adhd_hbq_8_T:weight_kg_BL_O) %>% 
  mutate_all(as.numeric) %>% 
  gather(domain_key, age, -ID) %>% 
  filter(!is.na(age)) %>% 
  ungroup()


```

# Create combined dataset

```{r}
d0_tidy <-
  d0_domains %>% 
  ungroup() %>% 
  full_join(d0_ages, by = c("ID", "domain_key")) %>% 
  separate(domain_key, into = c("domain", "measure", "wave", "informant")) %>%   
  dplyr::select(
    ID,
    wave,
    age,
    domain,
    measure,
    informant,
    value
  ) %>% 
  bind_rows(itsea) %>% 
  bind_rows(eeg)  %>% 
  mutate(
    domain = as.factor(domain),
    informant = as.factor(informant),
    wave = factor(
      wave,
      levels = c("BL", "30", "42", "54", "8", "12", "16"),
      labels = c("BL", "30", "42", "54", "8", "12", "16")
    )
  ) %>% 
  mutate(
    construct = case_when(
      domain == "adhd" | domain == "dsed" | domain == "extern" | 
        domain == "intern" | domain == "rad" ~ "psychopathology",
      domain == "head" | domain == "height" | domain == "weight" ~ "physical",
      domain == "iq" ~ "IQ",
      domain == "eeg" ~ "EEG"
    ),
    measure = if_else(
      (measure == "intsx" | measure == "p4nadz" | measure == "oddcdsx"),
      "papa", measure
    )
  ) %>% 
  mutate(
    ## 2020/04/14 identified error in data: IQ at 16-year wave for 150 is actually 160's score
    value = case_when(
      ID == 160 & wave == "16" & construct == "IQ" ~ 81, #(150's IQ score)
      ID == 150 & wave == "16" & construct == "IQ" ~ NA_real_,
      TRUE ~ value
    )
  ) %>% 
  mutate(
    wave = fct_relevel(
      wave,
      "BL", "30", "42", "54", "8", "12", "16"
    )
  ) %>% 
  # IDs not part of the sample
  filter(ID != 0 & ID < 800) %>% 
  arrange(ID, wave)

```

# Tidy age variables
```{r}
d0_tidy <- 
  d0_tidy %>% 
  rename(age_months = age) %>% 
  mutate(
    age_years = age_months / 12
  )
```

## Missing age data; impute
```{r}
d0_tidy %>% 
  filter(is.na(age_months)) %>% 
  arrange(ID, wave, domain, measure)

d0_tidy %>% 
  filter(is.na(age_months)) %>% 
  arrange(ID, wave, domain, measure) %>% 
  distinct(ID) %>% 
  arrange(ID) 

d0_tidy <-
  d0_tidy %>% 
  group_by(ID, wave) %>% 
  mutate(
    max_age_months_wave = max(age_months,  na.rm = TRUE),
    min_age_months_wave = min(age_months,  na.rm = TRUE),
    mean_age_years_wave = mean(age_years, na.rm = TRUE),
    mean_age_months_wave = mean(age_months, na.rm = TRUE),
    max_age_months_wave = if_else(
      max_age_months_wave == Inf, 
      mean_age_years_wave, max_age_months_wave
    ),
    min_age_months_wave = if_else(
      min_age_months_wave == Inf, 
      mean_age_years_wave, min_age_months_wave
    ),
    age_months = if_else(
      is.na(age_months), 
      mean_age_months_wave, age_months
    ),
    age_years = if_else(
      is.na(age_years), 
      mean_age_years_wave, age_years
    ),
    age_months = if_else(
      is.na(age_months), 
      mean_age_months_wave, age_months
    )
  ) %>% 
  filter(!is.na(age_years)) %>% 
  ungroup()
```

# Add additional predictors

```{r}
# remove SPSS labels from  variables
var_label(d0$group) <- NULL
var_label(d0$sex) <- NULL
var_label(d0$Ethnic) <- NULL

# select predictors
d_pred <-
  d0 %>% 
  dplyr::select(
    ID,
    male = sex,
    ethnic = Ethnic,
    gestation_weeks = Gestation,
    birth_weight = BW,
    inst_entry_age = Inst_ageM,
    FC_placement_age = FC_ageM, #Age in months when participant entered MacArthur FC
    stability_18,
    age_disrupt_days,
    group,
    bl_age_start,
    bl_age_end
  ) %>% 
  mutate(
    male = as.factor(male),
    group = as.factor(
      recode(
        group,
        "0" = "CAUG",
        "1" = "FCG",
        "2" = "NIG"
      )
    )
  )
```

# Tidy percent in institutionalized variables 
```{r}
d_pct_time <-
  d0 %>% 
  dplyr::select(
    ID, 
    pctinst_bsl:pctinst_16yr
  ) %>% 
  gather(wave, pctinst, -ID) %>% 
  mutate(
    wave = case_when(
      wave == "pctinst_bsl" ~ "BL",
      wave == "pctinst_30" ~ "30",
      wave == "pctinst_42" ~ "42",
      wave == "pctinst_54" ~ "54",
      wave == "pctinst_8yr" ~ "8",
      wave == "pctinst_12yr" ~ "12",
      wave == "pctinst_16yr" ~ "16"
    )
  ) %>% 
  filter(!is.na(pctinst)) %>% 
  arrange(ID, wave)
```

# Create variables to index missingness
```{r}
# count number of measures completed after baseline (max is 68 across all follow-up waves)
# and calculate % missing across all follow-up waves
missing_vars <-
  d0_tidy %>% 
  filter(wave != "BL") %>% 
  select(
    ID,
    wave,
    measure,
    domain,
    informant,
    value
  ) %>% 
  unite(measure, c(measure, domain, informant)) %>% 
  pivot_wider(
    names_from = c("measure", "wave")
  ) %>% 
  mutate(
    n_obs = pmap_dbl(
      select(., c(dai_dsed_P_30:hbq_intern_T_16)),
      function(...) sum(!is.na(c(...)), na.rm = TRUE)
    )
  ) %>% 
  select(
    ID,
    n_obs
  ) %>% 
  mutate(
    per_missing = 1 - (n_obs / 68)
  )
```

# Stability variables and final tidied dataset 
```{r}
d <-
  d0_tidy %>% 
  left_join(d_pred, by = "ID") %>% 
  left_join(d_pct_time, by = c("ID", "wave")) %>% 
  left_join(missing_vars, by = c("ID")) %>% 
  dplyr::select(
    ID,
    group,
    male,
    ethnic,
    gestation_weeks,
    birth_weight,
    inst_entry_age,
    FC_placement_age,
    stability_18,
    age_disrupt_days,
    wave,
    bl_age_start,
    bl_age_end,
    age_months, 
    age_years,
    mean_age_months_wave,
    mean_age_years_wave,
    max_age_months_wave,
    min_age_months_wave,
    construct,
    domain,
    measure,
    informant,
    value,
    pctinst,
    n_obs,
    per_missing
  )  %>% 
  group_by(ID) %>% 
  mutate(
    wave = factor(
      wave,
      levels = c("BL", "30", "42", "54", "8", "12", "16"),
      labels = c("BL", "30m", "42m", "54m", "8y", "12y", "16-18y")
    ),
    stability_18 = as.factor(
      case_when(
        stability_18 == "no" ~ "FCG, disrupted",
        stability_18 == "yes" ~ "FCG, stable",
        group == "CAUG" ~ "CAUG"
      )
    ),
    age_disrupt_months = age_disrupt_days / 30,
    # determine if FCG participant had been disrupted from original placement by the given wave; this is a within-person time-varying effect
    stable = case_when(
      round(age_months, 0) >= round(age_disrupt_months, 0) ~ "disrupted",
      round(age_months, 0) < round(age_disrupt_months, 0) ~ "stable",
      stability_18 == "FCG, stable" ~ "stable"
    ),
    stable_num = case_when(
     stable ==  "disrupted" ~ 0,
     stable == "stable" ~ 1
    )
  ) %>% 
  # remove duplicated row
  distinct(ID, wave, domain, value, informant, .keep_all = TRUE) %>% 
  dplyr::select(
    -stability_18
  ) %>% 
  ungroup()
```

# Add sibling information
```{r}
d <-
  d %>% 
  left_join(read_csv(sibling_file) %>% select(-group), by = "ID") %>% 
  mutate(
    family_id = if_else(
      is.na(family_id),
      ID, family_id
    )
  )
```

# Export data
```{r}
write_csv(d, paste0(home, "/data/BEIP_big_analysis_tidied_data_20221013.csv"))

#for public sharing
# d_share <-
#   d %>% 
#   group_by(ID) %>% 
#   mutate(
#     git_id = sample(1:50000, 1)
#   ) %>% 
#   ungroup() %>% 
#   dplyr::select(
#     git_id, 
#     everything(),
#     -ID,
#     -FC_placement_age
#   )
# 
# write_csv(d_share, paste0(home, "/data/king_BEIP_comphrensive_analysis_data_share.csv"))
```

